---
title: 'Part 1: Binary Logistic Regression'
author: "Sydney Rilum"
date: "1/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(jtools)
```

```{r}
#pairs plot (GGally)
penguins %>% 
  select(species, bill_length_mm:sex) %>% 
  ggpairs(aes(color = species))
```

Create a subset with only Adelie and Chinstrap penguins.
```{r}
adelie_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  mutate(species = fct_drop(species)) #factor drop drops any factor without observations

# IN CONSOLE: levels(adelie_chinstrap$species) ...see that Gentoo is still listed as a factor, so use fct_drop to fix that
```

Let's just dataviz of those two species:
```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = flipper_length_mm)) +
  geom_point(aes(color = sex)) +
  facet_wrap(~species)
```

Use binary logistic regression (2 possible outcomes) to determine probability based on several variables to determine if our penguin is Adelie or Chinstrap species.

Binary Logistic Regression variables:
- body mass
- flipper length
- penguin sex
```{r}
#glm() = general linear model
adelie_chinstrap_blr <- glm(species ~ body_mass_g + flipper_length_mm + sex,
                            data = adelie_chinstrap,
                            family = "binomial") # type of logistic regression
```

Take a look at the outcomes:
```{r}
adelie_chinstrap_blr

summary(adelie_chinstrap_blr)

# positive value for flipper length coefficient = odds of being chinstrap, with increase in flipper length, the odds that this is a chinstrap penguin increases
```

```{r}
ggplot(data = adelie_chinstrap, aes(x = species, y = flipper_length_mm)) +
  geom_jitter(aes(color = sex))

# as flipper length increases, chance it's a chinstrap penguin increases
```

What are the actual probabilities of being Chinstrap for each of the existing observations in our adelie_chinstrap data frame?

```{r}
blr_fitted <- adelie_chinstrap_blr %>% 
  broom::augment(type.predict = "response")

#`augment()` takes original data, adds on a coloumn for probability that this in a chinstrap penguin, based on our model = ".fitted" value that's a chance/% of being chinstrap

# a way to test our model, see we would get some false positives for chinstrap, when it's actually an adelie.... so how often is our model right?/wrong?...how can we improve that algorithm...machine learning

```

Plotting fitted probabilities:
```{r}
ggplot(data = blr_fitted, aes(x = flipper_length_mm, y = .fitted)) +
  geom_point(aes(color = sex,
                 pch = species)) + # point style classifier
  geom_smooth(aes(color = sex), se = FALSE) +
  labs(x = "Flipper lentgth (mm)",
       y = "Probability of outcome Chinstrap")
```

Plot model based on different variables:
```{r}
# gives you quick view of overall model trend for probability
effect_plot(adelie_chinstrap_blr,
            pred = flipper_length_mm, #predictor variable
            y.label = "Probability of Chinstrap",
            interval = TRUE) #adds confidence interval

effect_plot(adelie_chinstrap_blr,
            pred = body_mass_g, #predictor variable
            y.label = "Probability of Chinstrap",
            interval = TRUE) #adds confidence interval
```

What's the probability that a female penguin weighing 3410 g with a flipper length of 192mm is a Chinstrap?
```{r}
ex_1 <- predict(adelie_chinstrap_blr,
                data.frame(sex = "female",
                           body_mass_g = 3410,
                           flipper_length_mm = 192),
                type = "response") #gives you probability value instead of log odds value
ex_1
```



